### 2016-07-05 sections/image_texts/col3byall.tex
Update col3byall.tex
wording

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, here we show the result from increasing dimension of input data from Fig.~\ref{fig: only_pahs} to 25, gradually. The order of input data is the same as order of data in Fig.~\ref{fig: cor_cluster1}.}

>>>>

    \caption{Similar to Fig.~\ref{fig: all_derived_ones}, the result from gradually increasing the dimension of the input data from Fig.~\ref{fig: only_pahs} to 25. The order of the input data is the same as the order in Fig.~\ref{fig: cor_cluster1}.}
